---
title: "zipR demo"
author: "Leslie Huang"
date: "4/16/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introducing zipR: zip() for R

### Loading the library

```{r echo=TRUE}
library(devtools)

devtools::install_github("leslie-huang/zipR")

library(zipR)
```

### Dummy data
```{r echo=TRUE}
a <- c(1,2,3)
b <- c(4,5,6)
c <- c(1,2,3,4,5,6)
d <- c(7,8)
z <- c(9)
filler <- c(NA)
```

### zip two vectors of the same length

```{r}
zipr(a,b)

```


### zip two vectors of different lengths, repeating the shorter vector

`broadcast = TRUE` repeats elements of the shorter vector so that it is the same length as the longer vector
```{r}
zipr(a, z, broadcast = TRUE)

zipr(a, c, broadcast = TRUE)
```

### zip two vectors of different lengths, using the default fill value 

`fill = TRUE` without a `fillvalue` specified fills in the shorter vector with `NA`
```{r}
zipr(z, a, fill = TRUE)

```

### zip two vectors of different lengths, using a custom fill value
```{r}
zipr(c,a, fill = TRUE, fillvalue = z)

zipr(c,z, fill = TRUE, fillvalue = d)

```

