---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/leslie-huang/zipR.svg?branch=master)](https://travis-ci.org/leslie-huang/zipR)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/leslie-huang/zipR?branch=master&svg=true)](https://ci.appveyor.com/project/leslie-huang/zipR)


# zipR version 0.1.0

### An R library for zip()

This library does one thing, and one thing only: implementing Python-style* zip() for R.


### To install

`install.packages("zipR")`

\* without the functionality of iterators or tuples.


### Quick demo


```{r echo=FALSE}

library(zipR)
```


#### Dummy data

Some sequences of different lengths, in order to test the different options available in `zipr`.
```{r echo=TRUE}
a <- c(1,2,3)
b <- c(4,5,6)
c <- c(1,2,3,4,5,6)
d <- c(7,8)
z <- c(9)
filler <- c(NA)
```

#### zip two vectors of the same length

```{r}
zipR::zipr(a,b)

```


#### zip two vectors of different lengths, repeating the shorter vector

`broadcast = TRUE` repeats elements of the shorter vector so that it is the same length as the longer vector
```{r}
zipr(a, z, broadcast = TRUE)

zipr(a, c, broadcast = TRUE)
```

#### zip two vectors of different lengths, using the default fill value 

`fill = TRUE` without a `fillvalue` specified fills in the shorter vector with `NA`
```{r}
zipr(z, a, fill = TRUE)

```

#### zip two vectors of different lengths, using a custom fill value

```{r}
zipr(c,a, fill = TRUE, fillvalue = z)

zipr(c,z, fill = TRUE, fillvalue = d)

```

The demo for zipR is also available <a href="https://leslie-huang.github.io/zipr/zipr_demo.html">here</a>.
